An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-25 paper/paper.tex
Paper: rename project title
Paper: Write abstract, future work

\begin{abstract}
Abstract
\end{abstract}

@@

\chapter{Introduction}

@@

\subsection{The Metadata Layer} \label{subsec:TheMetadataLayer_sec:SystemDesign}
Due to time constraints, we simplified the implementation of the metadata layer of our system from a DHT to a tracker. As part of this simplification, we ensure that the tracker would not perform noticeably better than a DHT by not making obvious optimizations. To make the future transition to a DHT as easy as possible, we created a standard interface that our program uses to interact with a metadata layer, where each interface call is general enough to be implemented for any type of metadata layer implementation. The following operations are supported:
\begin{description}
\item[Join Network:] The peer registers itself with the overlay network, specifying what ID it wants to use.
\item[Find Closest Node:] Given a valid ID, return the closest ID that is registered in the network. This is used for finding nodes to replicate on. In our implementation this is accomplished via a binary search through the array of all registered keys, giving an average case search time of $O(\log n)$.
\item[Get:] Given an ID, return the Metadata Record of the corresponding node. This is most closely related to the standard get function used in hash tables.
\item[Blacklist Node:] When a peer performs this interface call, it adds its own ID to the list of blacklisters for a specified node.
\item[Backup File:] Register the creation of a newly-created backup with the metadata layer.
\item[Update File Size:] Let the metadata layer know that the size of a given file has changed.
\end{description}
Our tracker implementation is a standalone multithreaded application. It uses a custom threadpool implementation, called the Dispatcher, to accept several connections at a time from peers to process the interface calls listed above. Each Metadata Record is stored in an unordered map, which maps node IDs to their corresponding record.

@@

As it stands now, our system is unusable by a majority of Internet users, since they live behind routers with NAT. We need to design some mechanism to overcome this in our system. We can turn to Skype, BitTorrent, BitTorrent Sync, and other P2P applications for inspiration.

% TODO briefly explain what NAT is why and it makes P2P hard

@@

% TODO two reasons to find # reps: ensure availability in presence of different churn, and what is written below

@@

@@

\begin{itemize}
    \item Replace the centralized tracker with a DHT to become completely decentralized.
    \item Encrypted communication between peers to reduce information leakage.
    \item The ability to backup folders, not just files.
\end{itemize}

% TODO there are more things missing from impl

% TODO there are more things missing from spec

@@

\bibitem{dropboxusers} https://www.dropbox.com/news/company-info
\bibitem{pStore} C. Batten, K. Barr, A. Saraf, S. Trepetin, pStore: A Secure Peer-to-Peer Backup System
\bibitem{PeerStore} M. Landers, H. Zhang, K. Tan, PeerStore: Better Performance by Relaxing in Peer-to-Peer Backup
\bibitem{StorageSearchP2PNetworks} J. Augustine, A. Molla, E. Morsy, G. Pandurangan, Storage and Search in Dynamic Peer-to-Peer Networks
\bibitem{p2pSurvey} A. Passarella, A survey on content-centric technologies for the current Internet: CDN and P2P solutions
\bibitem{bittorrentDHT} http://www.bittorrent.org/beps/bep\_0005.html
\bibitem{btsynctech} http://www.bittorrent.com/sync/technology
\bibitem{btsyncuserguide} http://btsync.s3-website-us-east-1.amazonaws.com/BitTorrentSyncUserGuide.pdf
\bibitem{btsyncapi} http://www.bittorrent.com/sync/developers/api
\bibitem{bittorrentProtocol} http://www.bittorrent.org/beps/bep\_0003.html
\bibitem{cryptoDef} Rivest, Ronald L. (1990). "Cryptology". In J. Van Leeuwen. Handbook of Theoretical Computer Science 1. Elsevier.
\bibitem{syslogRFC1} C. Lonvick, "The BSD syslog Protocol". https://tools.ietf.org/html/rfc3164, August 2001.
\bibitem{syslogRFC2} R. Gerhards, "The syslog Protocol". https://tools.ietf.org/html/rfc5424, March 2009.

>>>>

\begin{abstract}
For many computer users, having access to a reliable file backup service is important. As computers and computer-related technologies improve, users have the ability to generate higher resolution content. Creating backups becomes less feasible as the amount of data grows; limited network bandwidth makes the backup process cumbersome, and access to a large amount of storage space for backups is either limited or expensive. In this report, we propose a new backup system, BTBackup, which aims to solve both problems. Our system is designed as a Peer-to-Peer (P2P) network, where users of the system use each other as backup locations. Users offer storage space that is proportional to the amount of data that they backup. This means that the capacity of each user's physical storage is the only limiting factor for how much they can back up. We solve the problem of long data transfers for big files by leveraging the speed offered by the BitTorrent Protocol, which uses a file chunking mechanism to download files from multiple peers at once. By testing our system in various scenarios, we show that it achieves our goal of quicker backup creation through the use of file transfer parallelization.
\end{abstract}

@@

% TODO: Talk about how fast transfer are important for P2P backup in particular, since many replicas will need to be made and replicas will need to be moved around.
\chapter{Introduction}

@@

\subsection{The Metadata Layer} \label{subsec:TheMetadataLayer_sec:SystemDesign}
Due to time constraints, we simplified the implementation of the metadata layer of our system from a DHT to a tracker. As part of this simplification, we ensure that the tracker would not perform noticeably better than a DHT by not making obvious optimizations. To make the future transition to a DHT as easy as possible, we created a standard interface that our program uses to interact with a metadata layer, where each interface call is general enough to be implemented for any type of metadata layer implementation. The following operations are supported:
\begin{description}
\item[Join Network:] The peer registers itself with the overlay network, specifying what ID it wants to use.
\item[Find Closest Node:] Given a valid ID, return the closest ID that is registered in the network. This is used for finding nodes to replicate on. In our implementation this is accomplished via a binary search through the array of all registered keys, giving an average case search time of $O(\log n)$.
\item[Get:] Given an ID, return the Metadata Record of the corresponding node. This is most closely related to the standard get function used in hash tables.
\item[Blacklist Node:] When a peer performs this interface call, it adds its own ID to the list of blacklisters for a specified node.
\item[Backup File:] Register the creation of a newly-created backup with the metadata layer.
\item[Update File Size:] Let the metadata layer know that the size of a given file has changed.
\item[Remove Backup:] Given a file ID and node ID, a peer can remove a specific replica of one of its files.
\end{description}
Our tracker implementation is a standalone multithreaded application. It uses a custom threadpool implementation, called the Dispatcher, to accept several connections at a time from peers to process the interface calls listed above. Each Metadata Record is stored in an unordered map, which maps node IDs to their corresponding record.

@@

We have designed our system so that peers directly contact each other by their IP address. While there are no problems with this solution when all peers are directly visible to the public Internet, it does pose a problem when they are behind a router that uses Network Address Translation, or NAT. When one or more hosts are behind a NAT-enabled router, they send network packets that have a destination outside of their subnet to the router. The router creates mappings between the hosts' internal IP address and the ports that they are using to the router's publicly visible IP address and a port that is chosen by the router. This is convenient for the typical home user, since Internet Service Providers typically only give one public IP address per Internet subscription. A home user can connect multiple devices to the NAT-enabled router, and they will all seem to be one device (with the router's public IP address) to the rest of the Internet. While it is convenient, it comes at the cost of not being able to initiate a connection to a device behind a NAT, since no IP/port mapping has been made yet. This is the case with most home users today, so we would need to design some mechanism to overcome this in our system if it were to be used by people all over the world. We can turn to Skype, BitTorrent, BitTorrent Sync, and other P2P applications for inspiration. These applications and protocols use mechanisms such as publicly visible supernodes as relay servers \cite{skypeSupernode}, trackers \cite{bittorrentProtocol}, and Universal Plug and Play (UPnP) \cite{btsynctech}.

@@

@@

Optimally, we would want to determine the minimum number of replicas needed in order to provide data availability while still taking advantage of the speed boost provided by BitTorrent. In order to determine this number, further tests could be done on our system that modifies the number of replicas that a peer seeks to create. The download and uploads speeds would then be measured for each replica count and compared to each other in order to determine if there are any differences. In order to also test data availability, the tests could factor in a rate of churn, similar to the test scenario described in section \ref{subsec:EffectsofChurn_sec:TestScenarios_chap:Methodology}. The availability of replicas would then be measured based on our system's challenge mechanism.

@@

\begin{itemize}
    \item Replace the centralized tracker with a DHT to become completely decentralized.
    \item Encrypted communication between peers to reduce information leakage. The actual transfer of data is encrypted; this refers to the transfer of encryption secrets and challenge messages.
    \item The ability to backup folders, not just files.
    \item Implement a more sophisticated challenge mechanism. Our current implementation of the challenge mechanism only checks for node availability. In order to have a system where all peers are storing the amount of data they are supposed to, the challenge mechanism we described in section \ref{subsec:ChallengeMechanism_sec:Fairness_chap:BTBackup} will need to be implemented.
    \item Use only open source software. Currently, BitTorrent Sync is closed source. In order to ensure that the system can be completely trusted, we would either need to wait for BitTorrent Sync to become open source, use an open source alternative, or create our own.
\end{itemize}

@@

\bibitem{dropboxusers} https://www.dropbox.com/news/company-info
\bibitem{pStore} C. Batten, K. Barr, A. Saraf, S. Trepetin, pStore: A Secure Peer-to-Peer Backup System
\bibitem{PeerStore} M. Landers, H. Zhang, K. Tan, PeerStore: Better Performance by Relaxing in Peer-to-Peer Backup
\bibitem{StorageSearchP2PNetworks} J. Augustine, A. Molla, E. Morsy, G. Pandurangan, Storage and Search in Dynamic Peer-to-Peer Networks
\bibitem{p2pSurvey} A. Passarella, A survey on content-centric technologies for the current Internet: CDN and P2P solutions
\bibitem{bittorrentDHT} http://www.bittorrent.org/beps/bep\_0005.html
\bibitem{btsynctech} http://www.bittorrent.com/sync/technology
\bibitem{btsyncuserguide} http://btsync.s3-website-us-east-1.amazonaws.com/BitTorrentSyncUserGuide.pdf
\bibitem{btsyncapi} http://www.bittorrent.com/sync/developers/api
\bibitem{bittorrentProtocol} http://www.bittorrent.org/beps/bep\_0003.html
\bibitem{cryptoDef} Rivest, Ronald L. (1990). "Cryptology". In J. Van Leeuwen. Handbook of Theoretical Computer Science 1. Elsevier.
\bibitem{syslogRFC1} C. Lonvick, "The BSD syslog Protocol". https://tools.ietf.org/html/rfc3164, August 2001.
\bibitem{syslogRFC2} R. Gerhards, "The syslog Protocol". https://tools.ietf.org/html/rfc5424, March 2009.
\bibitem{skypeSupernode} S. Guha, N. Daswani, R. Jain, "An Experimental Study of the Skype Peer-to-Peer VoIP System". http://saikat.guha.cc/pub/iptps06-skype/ .
